Thesis Title

### 2022-03-16 chapters/introduction.tex
Updates from Overleaf

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 1.png}
\caption{\textbf{World Health Organisation Global Priority Pathogens list.} This catalogue includes, besides \textit{Mycobacterium tuberculosis} considered the number one global priority, a list of twelve microorganisms grouped under three priority tiers according to their antimicrobial resistance: critical (\textit{Acinetobacter baumannii}, \textit{Pseudomonas aeruginosa} and \textit{Enterobacteriaceae}), high (\textit{Enterococcus faecium}, \textit{Helicobacter pylori}, \textit{Salmonella} species, \textit{Staphylococcus aureus}, \textit{Campylobacter} species and \textit{Neisseria gonorrhoeae}), and medium (\textit{Streptococcus pneumoniae}, \textit{Haemophilus influenzae} and \textit{Shigella} species). The major objective was to encourage the prioritisation of funding and incentives, align research and development priorities of public health relevance, and garner global coordination in the fight against antimicrobial resistant bacteria. Adapted from \cite{world_health_organization_prioritization_2017}.}
\label{fig:figure1}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 6 source/Figure 2.png}
\caption{\textbf{Principles of current processing of bacterial pathogens.} Schematic representation of the current workflow for processing samples for bacterial pathogens is presented, with high complexity and a typical timescale of a few weeks to a few months. Samples that are likely to be normally sterile are often cultured on rich medium that will support the grown of any culturable organism. Samples contaminated with colonising flora present a challenge for growing the infecting pathogen. Many types of culture media (referred to as selective media) are used to favour the growth of the suspected pathogen.
Once an organism is growing, the likely pathogens are then processed through a complex pathway that has many contingencies to determine species and antimicrobial susceptibility. Broadly, there are two approaches. One approach uses MALDI-TOF for species identification prior to setting up susceptibility testing. The other uses Gram staining followed by biochemical testing to determine species; susceptibility testing is often set up simultaneously with doing biochemical tests. Lastly, depending on the species and perceived likelihood of an outbreak, a small subset of isolates may be chosen for further investigation using a wide range of typing tests. Adapted from \cite{didelot_transforming_2012}}
\label{fig:figure2}
\end{figure*}

@@

>>>>

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 1.pdf}
\caption{\textbf{World Health Organisation Global Priority Pathogens list.} This catalogue includes, besides \textit{Mycobacterium tuberculosis} considered the number one global priority, a list of twelve microorganisms grouped under three priority tiers according to their antimicrobial resistance: critical (\textit{Acinetobacter baumannii}, \textit{Pseudomonas aeruginosa} and \textit{Enterobacteriaceae}), high (\textit{Enterococcus faecium}, \textit{Helicobacter pylori}, \textit{Salmonella} species, \textit{Staphylococcus aureus}, \textit{Campylobacter} species and \textit{Neisseria gonorrhoeae}), and medium (\textit{Streptococcus pneumoniae}, \textit{Haemophilus influenzae} and \textit{Shigella} species). The major objective was to encourage the prioritisation of funding and incentives, align research and development priorities of public health relevance, and garner global coordination in the fight against antimicrobial resistant bacteria. Adapted from \cite{world_health_organization_prioritization_2017}.}
\label{fig:figure1}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 2.pdf}
\caption{\textbf{Principles of current processing of bacterial pathogens.} Schematic representation of the current workflow for processing samples for bacterial pathogens is presented, with high complexity and a typical timescale of a few weeks to a few months. Samples that are likely to be normally sterile are often cultured on rich medium that will support the grown of any culturable organism. Samples contaminated with colonising flora present a challenge for growing the infecting pathogen. Many types of culture media (referred to as selective media) are used to favour the growth of the suspected pathogen.
Once an organism is growing, the likely pathogens are then processed through a complex pathway that has many contingencies to determine species and antimicrobial susceptibility. Broadly, there are two approaches. One approach uses MALDI-TOF for species identification prior to setting up susceptibility testing. The other uses Gram staining followed by biochemical testing to determine species; susceptibility testing is often set up simultaneously with doing biochemical tests. Lastly, depending on the species and perceived likelihood of an outbreak, a small subset of isolates may be chosen for further investigation using a wide range of typing tests. Adapted from \cite{didelot_transforming_2012}}
\label{fig:figure2}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 3.pdf}
\caption{\textbf{Principles of current processing of bacterial pathogens based on whole genome sequencing.} Schematic representation of the workflow for processing samples for bacterial pathogens after adoption of whole genome sequencing, with an expected timescale that could fit within a single day. The culture steps would be the same as currently used in a routine microbiology laboratory. Once a likely pathogen is ready for sequencing, DNA will be extracted, taking as little as 2 hours to prepare the DNA for sequencing.
After sequencing, the main processes for yielding information will be computational. Automated sequence assembly algorithms are necessary for processing the raw sequence data, from which species, relationship to other isolates of the same species, antimicrobial resistance profile and virulence gene content can be assessed. All the results will also be used for outbreak detection and infectious diseases surveillance. Adapted from \cite{didelot_transforming_2012}}
\label{fig:figure3}
\end{figure*}
